---
title: "Parliament Waffle Plots"
author: "Zoe Meers"
date: "22/05/2018"
output:
  html_document:
    toc: yes
    toc_depth: 4
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
source("geom_parliament_waffle.R")
load("election_data.rda")
election_data$government[is.na(election_data$government)] <- 0
library(tidyverse)
library(patchwork)
```

# Unique parliament layouts:

Monkey Cage article : https://www.washingtonpost.com/news/monkey-cage/wp/2017/03/04/these-5-designs-influence-every-legislature-in-the-world-and-tell-you-how-each-governs/?utm_term=.e1e1c1c3c37b

## Opposing benches parliament

### United Kingdom, Canada

#### Data
```{r}
ukresults <- election_data %>%
  filter(country == "UK" & 
           year == 2017)
ukresults$seats <- as.numeric(ukresults$seats)
ukresults$government[is.na(ukresults$government)] <- 0
left_parties <- c("Labour", 
                  "Scottish National Party", 
                  "Liberal Democrats", 
                  "Green", 
                  "Plaid Cymru", 
                  "Ind")
right_parties <- c("Conservative", 
                   "Democratic Unionist")
ukresults$location <-
  ifelse(ukresults$party_long %in% left_parties, "left",
    ifelse(ukresults$party_long %in% right_parties, "right",
      NA
    )
  )
ukresults_left <- ukresults %>%
  filter(location == "left")

ukresults_right <- ukresults %>%
  filter(location == "right")
```

#### Plot 
```{r}
leftside <- ggplot() +
  geom_parliament_waffle(
    type = "opposing_benches",
    seatspp = ukresults_left$seats,
    party_names = ukresults_left$party_long,
    parlrows = 10,
  ) +
  theme_parliament() +
  theme(legend.position = "left") +
  labs(colour = "", title = "Opposing benches parliament: Westminster") +
  scale_colour_manual(
    values = c(ukresults_left$colour),
    labels = c(ukresults_left$party_long),
    limits = c(ukresults_left$party_long)
  )

rightside <- ggplot() +
  geom_parliament_waffle(
    type = "opposing_benches",
    seatspp = ukresults_right$seats,
    party_names = ukresults_right$party_long,
    parlrows = 10
  ) +
  theme_parliament() +
  labs(colour = "") +
  scale_colour_manual(
    values = c(ukresults_right$colour),
    labels = c(ukresults_right$party_long),
    limits = c(ukresults_right$party_long)
  ) 


uk_parliament <- combine_opposingbenches(left = leftside, right = rightside)
uk_parliament
```


## Semicircle parliament
### EU, France, United States, and so on...

#### Data
```{r}
us_congress <- election_data %>%
  filter(country == "USA" & 
           year == "2016" & 
           house == "Representatives")
us_senate <- election_data %>%
  filter(country == "USA" & 
           year == "2016" & 
           house == "Senate")
```

#### Plot
```{r}
ggplot() +
  geom_parliament_waffle(
    type = "semicircle",
    totalseats = sum(us_congress$seats),
    parlrows = 10, 
    party_names = us_congress$party_long,
    seatspp = us_congress$seats
  ) +
  theme_parliament() +
  labs(colour = "", title = "United States Congress") +
  scale_colour_manual(
    values = us_congress$colour,
    labels = us_congress$party_long
  )
```

```{r}
ggplot() +
  geom_parliament_waffle(
    type = "semicircle",
    totalseats = sum(us_senate$seats),
    parlrows = 4, 
    party_names = us_senate$party_long,
    seatspp = us_senate$seats
  ) +
  theme_parliament() +
  labs(colour = "", title = "United States Senate") +
  scale_colour_manual(
    values = us_senate$colour,
    labels = us_senate$party_long
  )
```


## Horseshoe parliament
### Australia, New Zealand


#### Data
```{r}
australia <- election_data %>%
  filter(year == 2016 & 
           country == "Australia" & 
           house == "Representatives")
australia <- australia[c(1, 5, 6, 7, 4, 3, 2), ]
```


#### Plot
```{r}
ggplot() +
  geom_parliament_waffle(
    type = "horseshoe",
    totalseats = sum(australia$seats),
    parlrows = 4, 
    seatspp = australia$seats,
    party_names = australia$party_long
  ) +
  theme_parliament() +
  labs(colour = "", title = "Horseshoe parliament: Australia") +
  scale_colour_manual(
    values = australia$colour,
    labels = australia$party_long
  )
```

## Circle parliament

### old German Bundestag (find more modern examples).

If we can't find a good example, is it worth including?


## Classroom parliament

### China, Russia, North Korea

#### Data
```{r}
russia <- election_data %>%
  filter(country == "Russia", 
         year == "2016")
```

#### Plot
```{r}
ggplot() +
  geom_parliament_waffle(
    type = "classroom",
    seatspp = russia$seats,
    party_names = russia$party_long,
    parlrows = 10
  ) +
  theme_parliament() +
  scale_colour_manual(
    values = c(russia$colour),
    labels = c(russia$party_long),
    limits = c(russia$party_long)
  ) +
  labs(colour = "", title = "Russian Parliament")
```






